### 2025-01-23 ESC195 Lecture Notes/main.tex
added link to github
jan 22

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf ESC 195 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Caculus II, Winter 2024 \hfill ESC 195\\
\section{More on Integrals}
\subsection{Riemann Sum - Non-Uniform Petition}
\begin{example}
    Given the following definite integral:
    $$\int^2_0 \sqrt{x} dx$$, we cannot evaluate its Riemann sum with uniforms partition, since the series of root cannot be easily evaluated. 
\end{example}

@@

\paragraph{Surface Area of Revolution} Given the curve $C: y = f(x)$, the surface area of the curve between two points $a$ and $b$, where $y'(x)$ is continuous, we would like the compute the surface area of the curve:

@@

@@

>>>>

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf ESC 195 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Caculus II, Winter 2024 \hfill ESC 195\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\

\section{More on Integrals}
\subsection{Riemann Sum - Non-Uniform Petition}
\begin{example}
    Given the following definite integral:
    $$\int^2_0 \sqrt{x} dx$$, we cannot evaluate its Riemann sum with uniforms partition, since the series of root cannot be easily evaluated. 
\end{example}

@@

\paragraph{Surface Area of Revolution} Given the curve $C: y = f(x)$, we would like to compute the surface area of the curve between two points $a$ and $b$ when rotated about the $x$-axis:

@@

\paragraph{Riemann Sum} Given a tank rectangular with width defined by $w = f(x)$, we can take a horizontal slice, $x^\star$, of the tank to compute the force exerted on the tank by the water:
    F =\sum_{i=1}^n \rho g x_i f(x_i) \Delta x

@@

\subsection{Calculus with Parametric Curves}
\paragraph{Tangents} The tangent to a parametric curve $C$ at a point $t$ is given by:
    \frac{dy}{dx} = \frac{dy/dt}{dx/dt} = \frac{y'(t)}{x'(t)}
\paragraph{Equation of the Tangent} The equation of the tangent to a parametric curve $C$ at a point $t_0$ is given by:
    y'(t_0) (x-x(t_0)) - x'(t_0) (y-y(t_0)) = 0
Hence, if $x'(t_0) = 0$, we have a vertical tangent; if $y'(t_0) = 0$, we have a horizontal tangent. However, if $x'(t_0) = 0$ and $y'(t_0) = 0$, we have no information.
    Let $x = \sin 2t$, $y = \sin t$, we have:
        x'(t) &= 2\cos 2t, \\
        y'(t) &= \cos t
    \textbf{Vertical Tangent}: $2\cos 2t = 0 \Rightarrow t = \frac{\pi}{4} + \frac{n\pi}{2}$.
    \textbf{Horizontal Tangent}: $\cos t = 0 \Rightarrow t = \frac{\pi}{2} + n\pi$.
    \textbf{At $t = 0$} we have $x' = y' = 0$. Thus, we have no information. On the graph, we see that the curve intersects itself at $t = 0$.
\paragraph{Area under Parametric Curve} The area under a parametric curve $C$ between $t_1$ and $t_2$ is given by:
    A = \int^{x(t_2)}_{x(t_1)} y(x) \, dx = \int_{t_1}^{t_2} y(t) x'(t) \, dt 
\begin{definition}[Orientation]
    The orientation of a parametric curve $C$ is given by the direction of the curve as $t$ increases. If the enclosed area is to the left of the trace of $t$ (counter-clockwise) the orientation is positive; otherwise, it is negative.
\paragraph{} The sign of the area of a parametric curve $C$ is given by the orientation of the curve.
\paragraph{Area of Closed Curves} The area of a closed parametric curve $C$ is given by:
    A = \oiint_C dA = \int_{t_1}^{t_2} y(t) x'(t) \, dt = \int_{t_1}^{t_2} x(t) y'(t) \, dt
, where
\begin{equation*}
    x(t_1) = x(t_2), \quad y(t_1) = y(t_2) \quad \text{and} \quad \text{$t_2$ is the smallest $t>t_1$ to satisfy the condition}.
\end{equation*}
\paragraph{Arc Length} The arc length of a parametric curve $C$ is given by:
    L = \int_a^b \sqrt{\left(\frac{dx}{dt}\right)^2 + \left(\frac{dy}{dt}\right)^2} \, dt
    Given $x = t\cos t$, $y = t\sin t$, we have:
        \frac{dx}{dt} &= \cos t - t\sin t, \\
        \frac{dy}{dt} &= \sin t + t\cos t
    Thus, the arc length is given by:
        L &= \int_0^{2\pi} \sqrt{(\cos t - t\sin t)^2 + (\sin t + t\cos t)^2} \, dt \\
        &= \int_0^{2\pi} \sqrt{1 + t^2} \, dt
        \intertext{Using the substitution $t = \tan \theta$, we have:}
        &= \pi \sqrt{1 + 4\pi^2} + \frac{1}{2}\ln(2\pi + \sqrt{1 + 4\pi^2})
\paragraph{Surface Area of Revolution} The surface area of a parametric curve $C$ rotated about the $x$-axis is given by:
    A &= \int_a^b 2\pi y(t) ds \nonumber \\
    \intertext{From the arc length formula, we have $ds = \sqrt{(\frac{dx}{dt})^2 + (\frac{dy}{dt})^2} \, dt$, thus:}
    &= \int_a^b 2\pi y(t) \sqrt{\left(\frac{dx}{dt}\right)^2 + \left(\frac{dy}{dt}\right)^2} \, dt
Similarly, the surface area of a parametric curve $C$ rotated about the $y$-axis is given by:
    A = \int_a^b 2\pi x(t) \sqrt{\left(\frac{dx}{dt}\right)^2 + \left(\frac{dy}{dt}\right)^2} \, dt
\begin{example}[Surface Area of of a Ellipse]
    Given $x = a\sin t$, $y = b\cos t$, we have:
        \frac{dx}{dt} &= a\cos t, \\
        \frac{dy}{dt} &= -b\sin t
    Thus, the surface area of the ellipse is given by:
        A &= \int_0^{2\pi} 2\pi b\cos t \sqrt{a^2\cos^2 t + b^2\sin^2 t} \, dt \\
        &= 2\pi b \int_0^{2\pi} \sqrt{a^2 (1 - \sin^2 t) + b^2 \sin^2 t} \, dt \\
        &= 2\pi b \int_0^{2\pi} \sqrt{a^2 + b^2 - (a^2 - b^2)\sin^2 t} \, dt
    This has no analytical solution, but can be solved numerically. Typically, we take $\epsilon = \sqrt{\frac{a^2-b^2}{a^2}}$.

### 2025-01-23 MAT185 Lecture Notes/main.tex
added link to github
jan 22

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MAT 185 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Linear Algebra, Winter 2024 \hfill MAT 185\\
\section{Vector Space}
\begin{definition}[Vector Space in $\mathbb{R}$]
    This course concerns with real vector spaces. A vectors space, ${V}$, over $\mathbb{R}$ is a collection of \textbf{object} $\textbf{v} \in V$ s.t. the follow axioms are followed
    \begin{enumerate}
        \item \textbf{Addition Axioms}
        \begin{enumerate}
            \item \textbf{Closure Under Addition:} \\
            $\textbf{x}, \textbf{y} \in V \implies \textbf{x} + \textbf{y} \in V$

@@

\subsection{Linear combinations}
\begin{definition}[Linear Combination]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}$, then:
    \begin{align*}
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n
    \end{align*}
    is a linear combination of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\end{definition}
\begin{definition}[Linear independence]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}$. If the equation:
    \begin{align*}
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n = \textbf{0}
    \end{align*}
    has only the trivial solution $\alpha_1 = \alpha_2 = \ldots = \alpha_n = 0$.

    Then, $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are said to be linearly independent; otherwise, they are linearly dependent.
\end{definition}
\begin{definition}[Span]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$, then:
    \begin{align}
        \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = \left\{ \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n \, | \, \alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R} \right\}
    \end{align}
    is the set of all linear combinations of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\end{definition}
\end{document}

>>>>

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MAT 185 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Linear Algebra, Winter 2024 \hfill MAT 185\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\
\section{Vector Space}
\subsection{Foundamental Properties}
\begin{definition}[Vector Space in $\mathbb{R}$]
    This course concerns with real vector spaces. A vectors space, ${V}$, over $\mathbb{R}$ is a collection of \textbf{object} $\textbf{v} \in V$ s.t. the follow axioms are followed
    \begin{enumerate}
        \item \textbf{Addition Axioms}
        \begin{enumerate}
            \item \textbf{Closure Under Addition:} \\
            $\textbf{x}, \textbf{y} \in V \implies \textbf{x} + \textbf{y} \in V$

@@

\subsection{Linear combinations}
\begin{definition}[Linear Combination]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}$, then:
    \begin{align*}
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n
    \end{align*}
    is a linear combination of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\end{definition}
\begin{definition}[Linear independence]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}$. If and only if the equation:
    \begin{align*}
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n = \textbf{0}
    \end{align*}
    has \textbf{only} the trivial solution $\alpha_1 = \alpha_2 = \ldots = \alpha_n = 0$.

    Then, $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are said to be linearly independent; otherwise, they are linearly dependent.
\end{definition}

\begin{definition}[Span]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$, then:
    \begin{align}
        \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = \left\{ \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n \, | \, \alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R} \right\}
    \end{align}
    is the set of all linear combinations of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\end{definition}
\begin{definition}[Basis]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. If $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent and $\text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = V$, then $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ is a basis of $V$.
\end{definition}
\end{document}

### 2025-01-23 MSE160 Lecture Notes/main.tex
added link to github
jan 22

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MSE 160 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Molecules and Materials, Winter 2024 \hfill MSE 160\\
\begin{center}
\textit{"In this class we are mostly understanding solids''} \\ - Prof. \textsc{Scott Ramsay}
\end{center}
\vspace{10pt}
\section{Mechanical Behavior}
\paragraph{Classes of Materials} In this class, we look at three classes of materials (non-exhaustive):
\begin{itemize}
    \item \textbf{Metal} held together with metallic bonds, typically \textbf{ductile} and \textbf{conductive}.
    \item \textbf{Ceramics}  (often metal oxides [excp: diamond]) held together via covalent \& ionic bonds, typically \textbf{brittle} and \textbf{insulating}.
    \item \textbf{Polymers} Molecules (often hydrocarbons) typically \textbf{ductile} and \textbf{insulating}
\end{itemize}
\paragraph{Engineering Stress} For normal stress, we know that:
\begin{equation}
    \sigma = \frac{F}{A_0}
\end{equation}
\paragraph{Engineering Strein} Also:
\begin{equation}
    \epsilon = \frac{\Delta l}{l_0}
\end{equation}
\paragraph{Young's Moduclus} For elastic deformation, $E$, is given, by Hooke's Law, as follows:
\begin{equation}
    \sigma = E \epsilon
\end{equation}
\paragraph{Tensile Test} We apply force as to the ends of a dogbone-sample, with $l_0$ being the gauge length and $A_0$ being the area of the cross-section at the middle. 
\paragraph{Tensile Strein} Maximum tensile strain on the engineeging stress-strain curve.
\subsection{Understanding Elastic Properties in terms of Atomic Configuration}
\paragraph{Atomic Configuration} We can understand the elastic properties of a material by looking at the atomic configuration. Skemetically, we can represent the atomic configuration as a spring system:
\begin{enumerate}
    \item \textbf{Intial - Before Loading} Atoms are in equilibrium, with the interatomic forces being balanced.
    \item \textbf{Loading} We apply a force to the material, causing the atoms to move from their equilibrium positions. The bond stretches and the atoms move further apart.
    \item \textbf{Unloading} We remove the force, causing the atoms to return to their equilibrium positions. 
\end{enumerate}
\paragraph{Atom Positions} Elastic modulus is dependent on the atomic interatomic bonding force. Thus, The elastic modulus is prootionaly to the slope of the interatomic force-seperation curve.
\paragraph{Force-Seperation Curve} The force-seperation curve is a plot of the force between two atoms as a function of the distance between them. The slope of the curve is proportional to the elastic modulus near the equilibrium position.

@@

    \paragraph{Mass} The mass of the beam is given by:
    $$ m = \rho V = \rho A L $$
    \paragraph{Deflection} The deflection of the beam is given by:
    \begin{align*} 
        \delta &= \frac{FL^3}{48EI} 
        \intertext{For a beam with a rectangular cross-section, we have:}
        \delta &= \frac{FL^3}{48E} \cdot \frac{12}{bh^3} = \frac{FL^3}{4Ebh^3}  
        \intertext{We can set $b$ proportional to $h$:}
        \delta &= \frac{FL^3}{cE} \cdot \frac{1}{A^2},\quad \text{for some constant $c$} 
        \intertext{We can then isolate for $A$, the free variable, and minimize the mass via the objective equation $m = \rho A L$:}
        A &= \sqrt{\frac{FL^3}{cE\delta}} \\
        m &= \rho L \sqrt{\frac{FL^3}{cE\delta}} = \rho L \sqrt{\frac{FL^3}{cE\delta}}
        \intertext{Arrange into the form (functional)(geometric)(material):}
        m &= \left(\frac{F}{c\delta}\right)^\frac{1}{2} \cdot \left(L^\frac{5}{2}\right)\cdot\left(\frac{\rho}{E^\frac{1}{2}}\right)
    \end{align*}
\end{example}
\paragraph{Material Peformance Index} The material performance index is given by:
    \begin{equation}
        \text{Material Performance Index (MSI)} = \frac{E^\frac{1}{2}}{\rho}
\end{equation}
\paragraph{MPI Graph} We plot $\log E$ against $\log \rho$ to get the MPI graph. 
\paragraph{Tempered Glass} Temperglass are made to resist tension. It is done by applying a compressive stress to the surface of the glass. This is done by cooling the surface of the glass faster than the core or chemically treating the surface.
\appendix
\includepdf[pages=-, angle=90]{EquationSheet.pdf}
\end{document}

>>>>

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MSE 160 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Molecules and Materials, Winter 2024 \hfill MSE 160\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\
\begin{center}
\textit{"In this class we are mostly understanding solids''} \\ - Prof. \textsc{Scott Ramsay}
\end{center}
\vspace{10pt}
\section{Mechanical Behavior}
\paragraph{Classes of Materials} In this class, we look at three classes of materials (non-exhaustive):
\begin{itemize}
    \item \textbf{Metal} held together with metallic bonds, typically \textbf{ductile} and \textbf{conductive}.
    \item \textbf{Ceramics}  (often metal oxides [excp: diamond]) held together via covalent \& ionic bonds, typically \textbf{brittle} and \textbf{insulating}.
    \item \textbf{Polymers} Molecules (often hydrocarbons) typically \textbf{ductile} and \textbf{insulating}
\end{itemize}
\paragraph{Engineering Stress} For normal stress, we know that:
\begin{equation}
    \sigma = \frac{F}{A_0}
\end{equation}
\paragraph{Engineering Strein} Also:
\begin{equation}
    \epsilon = \frac{\Delta l}{l_0}
\end{equation}
\paragraph{Young's Moduclus} For elastic deformation, $E$, is given, by Hooke's Law, as follows:
\begin{equation}
    \sigma = E \epsilon
\end{equation}
\paragraph{Tensile Test} We apply force as to the ends of a dogbone-sample, with $l_0$ being the gauge length and $A_0$ being the area of the cross-section at the middle. 
\paragraph{Tensile Strein} Maximum tensile strain on the engineeging stress-strain curve.
\subsection{Understanding Elastic Properties in terms of Atomic Configuration}
\paragraph{Atomic Configuration} We can understand the elastic properties of a material by looking at the atomic configuration. Skemetically, we can represent the atomic configuration as a spring system:
\begin{enumerate}
    \item \textbf{Intial - Before Loading} Atoms are in equilibrium, with the interatomic forces being balanced.
    \item \textbf{Loading} We apply a force to the material, causing the atoms to move from their equilibrium positions. The bond stretches and the atoms move further apart.
    \item \textbf{Unloading} We remove the force, causing the atoms to return to their equilibrium positions. 
\end{enumerate}
\paragraph{Atom Positions} Elastic modulus is dependent on the atomic interatomic bonding force. Thus, The elastic modulus is prootionaly to the slope of the interatomic force-seperation curve.
\paragraph{Force-Seperation Curve} The force-seperation curve is a plot of the force between two atoms as a function of the distance between them. The slope of the curve is proportional to the elastic modulus near the equilibrium position.

@@

    \paragraph{Mass} The mass of the beam is given by:
    $$ m = \rho V = \rho A L $$
    \paragraph{Deflection} The deflection of the beam is given by:
        \delta = \frac{FL^3}{48EI} 
    \begin{align*} 
        \intertext{For a beam with a rectangular cross-section, we have:}
        \delta &= \frac{FL^3}{48E} \cdot \frac{12}{bh^3} = \frac{FL^3}{4Ebh^3}  
        \intertext{We can set $b$ proportional to $h$:}
        \delta &= \frac{FL^3}{cE} \cdot \frac{1}{A^2},\quad \text{for some constant $c$} 
        \intertext{We can then isolate for $A$, the free variable, and minimize the mass via the objective equation $m = \rho A L$:}
        A &= \sqrt{\frac{FL^3}{cE\delta}} \\
        m &= \rho L \sqrt{\frac{FL^3}{cE\delta}} = \rho L \sqrt{\frac{FL^3}{cE\delta}}
        \intertext{Arrange into the form (functional)(geometric)(material):}
        m &= \left(\frac{F}{c\delta}\right)^\frac{1}{2} \cdot \left(L^\frac{5}{2}\right)\cdot\left(\frac{\rho}{E^\frac{1}{2}}\right)
    \end{align*}
\end{example}
\paragraph{Material Peformance Index} The material performance index is given by:
        \text{Material Performance Index (MSI)} = \frac{E^\frac{1}{2}}{\rho}
\paragraph{MPI Graph} We plot $\log E$ against $\log \rho$ to get the MPI graph. 
\paragraph{Tempered Glass} Temperglass are made to resist tension. It is done by applying a compressive stress to the surface of the glass. This is done by cooling the surface of the glass faster than the core or chemically treating the surface.
\subsection{Density}
\paragraph{Density} The density of a material is given by:
    \rho = \frac{m}{V}
\paragraph{Archimedes' Principle} The buoyant force on an object is equal to the weight of the fluid displaced by the object. Derive from that, we have:
    \rho = \frac{m}{V} = \frac{m_{\text{object}}}{m_{\text{object}} - m_{\text{object in fluid}}}
\paragraph{Ordered structures} We have the following three orders:
    \item \textbf{Long Range Order (LRO)} Atoms are arranged in a well-defined pattern over long distances in repeating units. \\
    (Example) Diamonds, some polymers, most metals, many ceramics, graphite, quartz, etc.
    \item \textbf{Short Range Order (SRO)} Periodic arrangement of atoms over a few atomic or molecular spacings. \\
    (Example) Most polymers, glasses, amorphous materials, etc.
    \item \textbf{No Order (NO)} Atoms are randomly arranged. \\
    (Example) Ideal gases, etc.
\paragraph{Describing Crystal Structures} We can describe crystal structures by the following:
    \item \textbf{Unit Cell} The smallest repeating unit of a crystal structure that could be used to represent the entire crystal.
    \item \textbf{Lattice} The repeating arrangement of points that repersent the positions of atoms in the unit cell.\\
    (Example) Simple Cubic, Body-Centered Cubic, Face-Centered Cubic, etc.
    \item \textbf{Lattice Plus Basis} \textit{Not required for this course}
\paragraph{Theortical Density of Metals} The theoretical density of metals is given by:
    \rho = \frac{nM}{V_c N_A}
    \item $n$ is the number of atoms in the unit cell.
    \item $M$ is the atomic mass of the element (amu = g/mol).
    \item $V_c$ is the volume of the unit cell.
    \item $N_A$ is Avogadro's number ($6.022 \times 10^{23} \text{mol}^{-1}$)
\paragraph{Simple Cubic} The simple cubic structure has the following properties:
    \item \textbf{Centers of atoms} Located at the eight corners of a cube
    \item \textbf{Packing Density} Rare due to low packing density (only known example: Polonium, Po)
    \item \textbf{Close-packed directions} As cube edges.
    \item \textbf{Coordination Number} Number of nearest neighbor
\includepdf[pages=-, angle=90]{EquationSheet.pdf}
\end{document}

### 2025-01-23 linalgA1/main.tex
jan 22

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{250pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    Consider the augmented matrix of $\mathcal{A}$ and apply elementary row operations to obtain the RREF matrix of $\mathcal{A}$. For each elementary row operation, the set of solutions of $\mathcal{A}$ remains unchanged. Thus, $\mathcal{A}$ and $\mathcal{R}$ have the same set of solutions.
    %%% end of your answer  
}

@@

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{400pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    \paragraph{Additve Axioms}
    \begin{enumerate}
      \item By assumption, $\V_0$ is closed under vector addition. Thus, for all $\mathbf{u}, \mathbf{v} \in \V_0$, $\mathbf{u} + \mathbf{v} \in \V_0$.
      \item By assumption, $\V_0$ has the same vector addition as $\V$ and $\V$ is a vetor space. Thus, for all $\mathbf{u}, \mathbf{v}, \mathbf{w} \in \V_0$, $(\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})$.
      \item By assumption, $\V_0$ contains $\mathbf{0}$ and $\V$ is a vector space. Thus, for all $\mathbf{u} \in \V_0 \subseteq \V$, $\mathbf{u} + \mathbf{0} = \mathbf{u}$.
      \item For all $\textbf{u} \in \V_0 \subseteq \V$, a vector space. Under the usual scalar multiplication, $0\textbf{u} = \mathbf{0}$. With $(1 + (-1)) = 0$, we have:
      \begin{equation*}
        \begin{aligned}
          1\textbf{u} + (-1)\textbf{u} &= (1 + (-1))\textbf{u} \\
          &= 0\textbf{u} \\
          &= \mathbf{0}.
        \end{aligned}
      \end{equation*}
      Since $\V_0$ is closed under scalar multiplication, $(-1)\textbf{u} \in \V_0$. Thus, $\V_0$ contains the additive inverse of $\textbf{u}$.
      \end{enumerate}
    \paragraph{Scalar Multiplication Axioms}
    \begin{enumerate}
      \item By assumption, $\V_0$ is closed under scalar multiplication. Thus, for all $c \in \mathbb{R}$ and $\textbf{u} \in \V_0$, $c\textbf{u} \in \V_0$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $c, d \in \mathbb{R}$ and $\textbf{u} \in \V_0 \subseteq \V$, $(cd)\textbf{u} = c(d\textbf{u})$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $c \in \mathbb{R}$ and $\textbf{u}, \textbf{v} \in \V_0 \subseteq \V$, $c(\textbf{u} + \textbf{v}) = c\textbf{u} + c\textbf{v}$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $\textbf{u} \in \V_0 \subseteq \V$, $1\textbf{u} = \textbf{u}$.
    \end{enumerate}

@@

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{175pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    Given that $^2\mathbb{R}^2$ is a vector space, the set of $2 \times 2$ upper triangular real matrices is a subset of $^2\mathbb{R}^2$. Thus, we prove that $\V$ is a vector space of $^2\mathbb{R}^2$ by showing subspace test holds.
    \begin{enumerate}
      \item $\mathbf{0} \in \V$: $\mathbf{0}$ is an upper triangular matrix with $\textbf{0} = \begin{bmatrix}
        0 & 0 \\
        0 & 0
      \end{bmatrix}$. Given usual entry-wise addition, for all $\textbf{A} \in \V$, $\textbf{A} + \textbf{0} = \begin{bmatrix}
        a_{11} + 0 & a_{12} + 0 \\
        0 & a_{22} + 0
      \end{bmatrix} = \textbf{A}$. Thus, $\mathbf{0} \in \V$.
      \item Closure under addition: Let $A, B \in \V$. Then $A + B = \begin{bmatrix}
        a_{11} + b_{11} & a_{12} + b_{12} \\
        0 & a_{22} + b_{22}
      \end{bmatrix}$. So $A + B$ is upper triangular, and $A + B \in \V$.
      \item Closure under scalar multiplication: Let $A \in \V$ and $c \in \mathbb{R}$. Then $cA = \begin{bmatrix}
        ca_{11} & ca_{12} \\
        0 & ca_{22}
      \end{bmatrix}$. So $cA$ is upper triangular, and $cA \in \V$.
    \end{enumerate}

>>>>

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{250pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    Consider the augmented matrix of $\mathcal{A}$ and apply elementary row operations to obtain the RREF matrix of $\mathcal{A}$. For each elementary row operation, the set of solutions of $\mathcal{A}$ remains unchanged. This is proven in the previous parts.
    Thus, $\mathcal{A}$ and $\mathcal{R}$ have the same set of solutions.
    %%% end of your answer  
}

@@

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{400pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    \paragraph{Additve Axioms}
    \begin{enumerate}
      \item By assumption, $\V_0$ is closed under vector addition. Thus, for all $\mathbf{u}, \mathbf{v} \in \V_0$, $\mathbf{u} + \mathbf{v} \in \V_0$.
      \item By assumption, $\V_0$ has the same vector addition as $\V$ and $\V$ is a vetor space. Thus, for all $\mathbf{u}, \mathbf{v}, \mathbf{w} \in \V_0$, $(\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})$.
      \item By assumption, $\V_0$ contains $\mathbf{0}$ and $\V$ is a vector space. Thus, for all $\mathbf{u} \in \V_0 \subseteq \V$, $\mathbf{u} + \mathbf{0} = \mathbf{u}$.
      \item For all $\textbf{u} \in \V_0 \subseteq \V$, a vector space. Under the usual scalar multiplication, $0\textbf{u} = \mathbf{0}$. With $(1 + (-1)) = 0$, we have:
      \begin{equation*}
        \begin{aligned}
          1\textbf{u} + (-1)\textbf{u} &= (1 + (-1))\textbf{u} \\
          &= 0\textbf{u} \\
          &= \mathbf{0}.
        \end{aligned}
      \end{equation*}
      Since $\V_0$ is closed under scalar multiplication, $(-1)\textbf{u} \in \V_0$. Thus, $\V_0$ contains the additive inverse of $\textbf{u}$.
      \end{enumerate}
    \paragraph{Scalar Multiplication Axioms}
    \begin{enumerate}
      \item By assumption, $\V_0$ is closed under scalar multiplication. Thus, for all $c \in \mathbb{R}$ and $\textbf{u} \in \V_0$, $c\textbf{u} \in \V_0$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $c, d \in \mathbb{R}$ and $\textbf{u} \in \V_0 \subseteq \V$, $(cd)\textbf{u} = c(d\textbf{u})$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $c \in \mathbb{R}$ and $\textbf{u}, \textbf{v} \in \V_0 \subseteq \V$, $(c + d)\textbf{u} = c\textbf{u} + d\textbf{u}$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $\textbf{u} \in \V_0 \subseteq \V$, $1\textbf{u} = \textbf{u}$.
    \end{enumerate}

@@

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{175pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    We have the following:
    \paragraph{Additive Axioms}
    \begin{enumerate}
      \item For all $A, B \in \V$, $A + B = \begin{bmatrix}
        a_{11} + b_{11} & a_{12} + b_{12} \\
        0 & a_{22} + b_{22}
      \end{bmatrix}$ is upper triangular.
      \item For all $A, B, C \in \V$, for $(A+B)+C$, we have:
      \begin{equation*}
      \begin{aligned}
        (A+B)+C &= \begin{bmatrix}
          a_{11} + b_{11} & a_{12} + b_{12} \\
          0 & a_{22} + b_{22}
        \end{bmatrix} + C \\
        &= \begin{bmatrix}
          a_{11} + b_{11} + c_{11} & a_{12} + b_{12} + c_{12} \\
          0 & a_{22} + b_{22} + c_{22}
        \end{bmatrix} 
        = A + \begin{bmatrix}
          b_{11} + c_{11} & b_{12} + c_{12} \\
          0 & b_{22} + c_{22}
        \end{bmatrix} \\
        &= A + (B+C).
      \end{aligned}
    \end{equation*}
      \item $\mathbf{0}$ is upper triangular. We take $\textbf{0} = \begin{bmatrix}
        0 & 0 \\
        0 & 0
      \end{bmatrix}$. For all $A \in \V$, $A + \textbf{0} = \begin{bmatrix}
        a_{11} + 0 & a_{12} + 0 \\
        0 & a_{22} + 0
      \end{bmatrix} = A$.
      \item For all $A \in \V$, We take another upper triangular matrix $-A = \begin{bmatrix}
        -a_{11} & -a_{12} \\
        0 & -a_{22}
      \end{bmatrix}$. For all $A \in \V$, $A + (-A) = \begin{bmatrix}
        a_{11} - a_{11} & a_{12} - a_{12} \\
        0 & a_{22} - a_{22}
      \end{bmatrix} = \textbf{0}$.
    \end{enumerate}
    \paragraph{Scalar Multiplication Axioms}
    \begin{enumerate}
      \item For all $A \in \V$, $c \in \mathbb{R}$, $cA = \begin{bmatrix}
        ca_{11} & ca_{12} \\
        0 & ca_{22}
      \end{bmatrix}$ is upper triangular. So $cA \in \V$.
      \item For all $A \in \V$, $c(dA) = \begin{bmatrix}
        cda_{11} & cda_{12} \\
        0 & cda_{22}
      \end{bmatrix} = (cd)A$.
      \item For all $A \in \V$, $(c+d)A = \begin{bmatrix}
        (c+d)a_{11} & (c+d)a_{12} \\
        0 & (c+d)a_{22} \end{bmatrix} = \begin{bmatrix}
          ca_{11} & ca_{12} \\
          0 & ca_{22}
        \end{bmatrix} + \begin{bmatrix}
          da_{11} & da_{12} \\
          0 & da_{22}
        \end{bmatrix} = cA + dA$.
      \item For all $A \in \V$, $1A = \begin{bmatrix}
        1a_{11} & 1a_{12} \\
        0 & 1a_{22}
      \end{bmatrix} = A$.
    \end{enumerate}
